---
title: "PWT Growth Graphs"
author: Tobias Yanchunas
output: 
  ioslides_presentation: 
    transition: 0
date: "Feb 27, 2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven) # for importing Stata data
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
knitr::opts_knit$set(root.dir=file.choose())
# CHANGE PATH
```

## "Graph 4 countries" code
```{r, echo = TRUE}
d <- read_stata("pwt1001.dta")
d <- d %>% mutate(lrgdppc = log(rgdpo/pop))

### Graph 4 countries function
graph4 <- function(c1, c2, c3, c4){
  d1 <- d %>% filter(countrycode==c1 | countrycode==c2 | countrycode==c3 | countrycode == c4)
  ggplot(d1, aes(x= year, y = lrgdppc, colour = countrycode)) +
    geom_line(linewidth = 1) + 
    geom_hline(yintercept=8,linetype=2) + 
    geom_hline(yintercept = 10, linetype = 2) +
    ylim(5,13.2) + xlim(1950, 2020) + ggtitle("Log rGDP per capita") +
    scale_color_manual(values=c('red', "blue", 'black', 'darkgrey'))
}
```


## ABW and AGO and AIA - 1
```{r, echo = F, warning = FALSE}
graph4("USA", "ABW", "AGO", "AIA")

```

## ALB and ARE and ARM - 2
```{r, echo = F, warning = F}
graph4("USA", "ALB", "ARE", "ARM")

```

## ATG and AUS and AUT - 3
```{r, echo = F, warning = F}
graph4("USA", "ATG", "AUS", "AUT")

```

## AZE and BDI and BEL - 4
```{r, echo = F, warning = F}
graph4("USA", "AZE", "BDI", "BEL")

```

## BEN and BFA and BGD - 5
```{r, echo = F, warning = F}
graph4("USA", "BEN", "BFA", "BGD")

```

## BGR and BHR and BHS - 6
```{r, echo = F, warning = F}
graph4("USA", "BGR", "BHR", "BHS")

```

## BIH and BLR and BLZ - 7
```{r, echo = F, warning = F}
graph4("USA", "BIH", "BLR", "BLZ")

```

## BMU and BOL and BRB - 8
```{r, echo = F, warning = F}
graph4("USA", "BMU", "BOL", "BRB")

```

## BRN and BTN and BWA - 9
```{r, echo = F, warning = F}
graph4("USA", "BRN", "BTN", "BWA")

```

## CAF and CHE and CHL - 10
```{r, echo = F, warning = F}
graph4("USA", "CAF", "CHE", "CHL")

```

## CIV and CMR and COD - 11
```{r, echo = F, warning = F}
graph4("USA", "CIV", "CMR", "COD")

```

## COG and COM and CPV - 12
```{r, echo = F, warning = F}
graph4("USA", "COG", "COM", "CPV")

```

## CRI and CUW and CYM - 13
```{r, echo = F, warning = F}
graph4("USA", "CRI", "CUW", "CYM")

```

## CYP and CZE and DJI - 14
```{r, echo = F, warning = F}
graph4("USA", "CYP", "CZE", "DJI")

```

## DMA and DNK and DOM - 15
```{r, echo = F, warning = F}
graph4("USA", "DMA", "DNK", "DOM")

```

## DZA and ECU and EST - 16
```{r, echo = F, warning = F}
graph4("USA", "DZA", "ECU", "EST")

```

## FIN and FJI and GAB - 17
```{r, echo = F, warning = F}
graph4("USA", "FIN", "FJI", "GAB")

```

## GEO and GHA and GIN - 18
```{r, echo = F, warning = F}
graph4("USA", "GEO", "GHA", "GIN")

```

## GNB and GNQ and GRC - 19
```{r, echo = F, warning = F}
graph4("USA", "GNB", "GNQ", "GRC")

```

## GRD and GTM and GUY - 20
```{r, echo = F, warning = F}
graph4("USA", "GRD", "GTM", "GUY")

```

## HND and HRV and HUN - 21
```{r, echo = F, warning = F}
graph4("USA", "HND", "HRV", "HUN")

```

## IDN and IRL and IRN - 22
```{r, echo = F, warning = F}
graph4("USA", "IDN", "IRL", "IRN")

```

## IRQ and ISL and ISR - 23
```{r, echo = F, warning = F}
graph4("USA", "IRQ", "ISL", "ISR")

```

## JAM and JOR and KAZ - 24
```{r, echo = F, warning = F}
graph4("USA", "JAM", "JOR", "KAZ")

```

## KGZ and KHM and KNA - 25
```{r, echo = F, warning = F}
graph4("USA", "KGZ", "KHM", "KNA")

```

## KWT and LAO and LBN - 26
```{r, echo = F, warning = F}
graph4("USA", "KWT", "LAO", "LBN")

```

## LBR and LCA and LKA - 27
```{r, echo = F, warning = F}
graph4("USA", "LBR", "LCA", "LKA")

```

## LSO and LTU and LUX - 28
```{r, echo = F, warning = F}
graph4("USA", "LSO", "LTU", "LUX")

```

## LVA and MAC and MAR - 29
```{r, echo = F, warning = F}
graph4("USA", "LVA", "MAC", "MAR")

```

## MDA and MDG and MDV - 30
```{r, echo = F, warning = F}
graph4("USA", "MDA", "MDG", "MDV")

```

## MKD and MLI and MLT - 31
```{r, echo = F, warning = F}
graph4("USA", "MKD", "MLI", "MLT")

```

## MMR and MNE and MNG - 32
```{r, echo = F, warning = F}
graph4("USA", "MMR", "MNE", "MNG")

```

## MOZ and MRT and MSR - 33
```{r, echo = F, warning = F}
graph4("USA", "MOZ", "MRT", "MSR")

```

## MUS and MWI and MYS - 34
```{r, echo = F, warning = F}
graph4("USA", "MUS", "MWI", "MYS")

```

## NAM and NER and NGA - 35
```{r, echo = F, warning = F}
graph4("USA", "NAM", "NER", "NGA")

```

## NIC and NLD and NPL - 36
```{r, echo = F, warning = F}
graph4("USA", "NIC", "NLD", "NPL")

```

## NZL and OMN and PAK - 37
```{r, echo = F, warning = F}
graph4("USA", "NZL", "OMN", "PAK")

```

## PAN and PER and PHL - 38
```{r, echo = F, warning = F}
graph4("USA", "PAN", "PER", "PHL")

```

## POL and PRT and PRY - 39
```{r, echo = F, warning = F}
graph4("USA", "POL", "PRT", "PRY")

```

## PSE and QAT and ROU - 40
```{r, echo = F, warning = F}
graph4("USA", "PSE", "QAT", "ROU")

```

## RWA and SAU and SDN - 41
```{r, echo = F, warning = F}
graph4("USA", "RWA", "SAU", "SDN")

```

## SEN and SLE and SLV - 42
```{r, echo = F, warning = F}
graph4("USA", "SEN", "SLE", "SLV")

```

## SRB and STP and SUR - 43
```{r, echo = F, warning = F}
graph4("USA", "SRB", "STP", "SUR")

```

## SVK and SVN and SWZ - 44
```{r, echo = F, warning = F}
graph4("USA", "SVK", "SVN", "SWZ")

```

## SXM and SYC and SYR - 45
```{r, echo = F, warning = F}
graph4("USA", "SXM", "SYC", "SYR")

```

## TCA and TCD and TGO - 46
```{r, echo = F, warning = F}
graph4("USA", "TCA", "TCD", "TGO")

```

## TJK and TKM and TTO - 47
```{r, echo = F, warning = F}
graph4("USA", "TJK", "TKM", "TTO")

```

## TUN and TZA and UGA - 48
```{r, echo = F, warning = F}
graph4("USA", "TUN", "TZA", "UGA")

```

## UKR and URY and UZB - 49
```{r, echo = F, warning = F}
graph4("USA", "UKR", "URY", "UZB")

```

## VCT and VEN and VGB - 50
```{r, echo = F, warning = F}
graph4("USA", "VCT", "VEN", "VGB")

```

## YEM and ZMB and ZWE - 51
```{r, echo = F, warning = F}
graph4("USA", "YEM", "ZMB", "ZWE")

```
