---
title: "Summary Statistics for Catagorizing Countries"
output: ioslides_presentation
author: Tobias Yanchunas
date: "2025-04-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven) # for importing Stata data
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)

setwd("/Users/tobyyanchunas/Desktop/REU_Wu")
d <- read_stata("pwt1001_typed.dta")


```

## Notes

- This relies on having the Penn World Table data (Table 10.01) already typed
  - Run through the "catagorizing_countries.R" file
  - We used the version published Jan 23, 2023
  - It was asked to reference: Feenstra, Robert C., Robert Inklaar and Marcel P. Timmer (2015), "The Next Generation of the Penn World Table" American Economic Review, 105(10), 3150-3182, available for download at www.ggdc.net/pwt
  
  
## Histogram of Types

```{r, echo = F, warning =F}
d2 <- d %>% filter(year == 2000) #Arbitrary year just to get one entry per country
#type0s = nrow(d2 %>% filter(type == 0))
#type1s = nrow(d2 %>% filter(type == 1))
#type2s = nrow(d2 %>% filter(type == 2))
#type3s = nrow(d2 %>% filter(type == 3))
#type4s = nrow(d2 %>% filter(type == 4))
#type5s = nrow(d2 %>% filter(type == 5))
#type6s = nrow(d2 %>% filter(type == 6))
#type7s = nrow(d2 %>% filter(type == 7))

ggplot(data = d2, aes(x = type))+
  geom_histogram(binwidth = 1, color = 'grey', fill = 'blue') + 
  ylab('Number of Countries') + 
  annotate("label", x = .5, y = 39, 
  label = "Type Zero's: 4
Type One's: 22
Type Two's: 18
Type Three's: 53
Type Four's: 12
Type Five's: 44
Type Sixes: 21
Type Seven's: 9") + 
  ggtitle("Histogram of Countries by Type") + 
  theme(axis.text.x = element_text(face="bold", color="black", size=10),
        axis.text.y = element_text(face="bold", color="black", size=10)) + scale_x_continuous(name = 'Type', breaks = c(0,1,2,3,4,5,6,7))

```

* 183 Total Countries

## Average of each Type
```{r, warning = FALSE, echo = F, message = F}
d3 <- d %>% drop_na(lrgdppc)
d3 <- d3 %>% group_by(type, year) %>% summarize(avg_lrgdppc = mean(lrgdppc))

ggplot(data = d3, aes(x=year, y = avg_lrgdppc, color = as.factor(type)))+
  geom_line(size = 1)+
  scale_color_manual(values=c('blue', "black", 'forestgreen','#d62728',
                              '#ff7f0e','#8c564b','#e377c2','#7f7f7f'))+
  ylim(5,13.2) + xlim(1950, 2020) + ggtitle("Log rGDP per capita", subtitle='
  Average Values of each Year per Type') +
  ylab('Average log rGDP pc') + 
  labs(color = "Types") + 
  geom_hline(yintercept=8,linetype=2, alpha = .3) + 
  geom_hline(yintercept = 10, linetype = 2, alpha = .3) 

#1f77b4 blue
#2ca02c green
#ff7f0e
#9467bd
```

* Each point was constructed as the average of each year within each type.


